\Large\textbf{Decentralized Data Marketplace to Enable Trusted Machine Economy}

### 2019-10-26 paper.tex
Append conclusion

\section{\normalsize\textbf{Future Work}}
%Data Auction
The data auction process is a data trading mechanism and an economically-driven scheme that establishes corresponding prices of data products through bidding process between consumers and providers. While there has been many auction models\cite{BigPicDataMarket} in several areas, only minimal research focus on third-party auction platforms. Our proposed decentralized data marketplace protects the privacy of participants which reveals the minimum information for validation and reduces the suspicion of trust to centralized parties or auctioneers. However, the auction process between multiple participants, analysis of potential threats and an overall game theory evaluation are still critical issues that need to be resolved.

>>>>

\section{\normalsize\textbf{Conclusion and Future Work}}
To our knowledge, this paper is the first attempt to construct fully decentralized data marketplaces with strong data integrity and transparency in mind.
The data auction process is a data trading mechanism and an economically-driven scheme that establishes corresponding prices of data products through bidding process between consumers and providers. While there have been various auction models\cite{BigPicDataMarket} in several areas, only few researches focus on third-party auction platforms. Our proposed decentralized data marketplace protects the privacy of participants which reveals the minimum information for validation and reduces the suspicion of trust to centralized parties or auctioneers. However, the auction process between multiple participants, analysis of potential threats and an overall game theory evaluation are still critical issues that need to be resolved.
